Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-20 article/article.Rmd
Commit 2024-05-17 13:12
Commit 2024-05-17 14:14
Commit 2024-05-20 11:19

>>>>

<!--
# Kazadzis2007 - Nine years of UV aerosol optical depth measurements at Thessaloniki, Greece
# From Stelios' paper 2007:
# AOD @340 from Brewer 086
# Period: 1997-2005
# The mean AOD for this period was calculated to 0.403 for the Brewer and 0.422 for the CIMEL.
# A linear regression on the Brewer deseasonalized data reveals a change of −3.8±0.93% per year.
# From the above data AOD @340 changes by 0.0153 per year (or 0.138 for the 9 years).
# Using Angstrom a= 1.6  this translates to a change in Angstrom β=0.00272 per year (or β=0.084 in 1997 and β=0.059 in 2005).
-->
